paper1_figures

### 2023-09-22 paper1_markdown.Rmd
22.09

-   But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation

```{=html}
<!-- -->
```
-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons

@@

## Reward and punishment

Possible introduction: Incentives are divided in reward and punishments. Punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015]. The positive effect of punishment in promoting cooperation is well confirmed ...

@@

@Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition

@Kingsley2016: the possibility of punish others increased the cooperation in homogeneous groups (= where all members started with the same endowment), but not in heterogeneous groups

@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)

@Balliet2011a: PUN: positive effect on cooperation in social dilemmas\
stronger if the punishment was costly (vs free)\
stronger if decentralized (vs centralized)\
stronger if SD with partners (vs strangers)\
stronger if iterated (vs one-shot)\
REWARD: positive effect on cooperation in social dilemmas\
stronger if costly vs free\
no effect of de-centralized\
stronger if iterated (vs one-shot)\
stronger in the resource dilemma (vs public good or prisoner dilemma)\
OVERALL: no difference on the strength of these effects

>>>>

-   But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons

@@

## Incentives

Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^1]. In the litterature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual. In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g. @Pfattheicher2018; @Balliet2011a].

[^1]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.

However, this main results is subjected to several moderator factors. First, the punishment have a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008]. Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a]. Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016]. To add: @Chen2022 low members do not punish others low members --\> solidarity that encourages free-riding??

moderators:

@Egas2008: punishment must be not too costly and highly effective

after the moderators: say that we must be cautious and cite rockenbach + cite the problems

problem:

-   second order social dilemma @Milinski2012

-   anti social punishment

solution = democratic, rather than peer, punishment: @Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition

However, a system in which every individual has the possibility to assign a punishment to others can entail a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators

@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)

@@

@Milinski2012:  + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it)

@Balliet2011a: \
REWARD: positive effect on cooperation in social dilemmas\
stronger if costly vs free\
no effect of de-centralized\
stronger if iterated (vs one-shot)\
stronger in the resource dilemma (vs public good or prisoner dilemma)\
OVERALL: no difference on the strength of these effects

@Pfattheicher2018: democratic (vs peer) punishment showed lower punishment level, less antisocial punishment and higher final payoff and higher cooperation levels + the payoff was highest in a control condition, so higher cooperation cannot fully compensate punishment cost (although democratic could be worthy on the long run)

@Irwin2014: punishment and reward have detrimental effects on cooperation + trust

@Nelissen2013: social punishment = disapproval is better than financial because cooperation rates do not drop after the removal
